Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics{figures/sample_sequence.eps}
    \caption{Each scenario iterated through 256 combinations of strategy implementation.}
    \label{fig:sample_sequence}
\end{figure}

@@

\subsubsection*{Retrofit and New Development Trajectory}
The majority of Wesbrook has been completed as of 2020, with 50\% of the total expected build-out of 725,925 sqm. remaining between now and the mid-21st century. As indicated in Figure \ref{fig:wesbrook_base} the yet-to-be-completed development will be assessed in the model through the future periods. While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{Wesbrook masterplan}. The simulation framework is built from a baseline in 2020 of the completed development up to 2020. Two more time periods were simulated, the first in 2050 and then in 2080. The base-case for each time period assumes that the stock of buildings that were simulated in the previous time-step (existing) were retrofitted with similarly performing technologies and components. New buildings are however built to a performance profile modeled after the code trajectory referenced in Table \ref{tab:code_trajectory}. While it is expected that the future will hold more advanced technologies, code development is capped at the introduction of the NZER requirements.

\begin{table*}[h]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{The first two-column table.}
    \label{tab:code_trajectory}
    \centering
    \begin{tabular}{ | c | c | c | }
        \hline
        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
        \hline
        Entry 1 & Entry 2 & Entry 3 \\
        \hline
    \end{tabular}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table*}

@@

The UBEMs are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits, described in full in Table \ref{tab:model_parameters}.

\begin{table}[ht]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{Example of a table.}
    \label{tab:model_parameters}
    \centering
    \begin{tabular}{| c | c | c | }
        \hline
        \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
        \hline
        Entry 1 & Entry 2 & Entry 3 \\
        \hline
    \end{tabular}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table}

@@

%---------------------------------------------------------------------------------------
\section*{Results}
The simulation procedure was executed for 1024 iterations, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic.

\subsection*{General Performance}
Figure \ref{fig:joint_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios. Climate change does not appear to have a large impact on decarbonisation efforts. A warmer climate may even contribute to more emissions-performance at a lower cost.

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1.0]{figures/general_results.eps}
    \caption{General results from the iterations.}
    \label{fig:joint_plot}
\end{figure}

@@

MACCs were drawn as another form of visualising decision making. Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the bars. However, it improves on previous \textit{illustrative} MACCs in that the bars do not unnecessarily represent single strategy interventions, but rather a set of strategies. It was drawn to assist in planning under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies. The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting XXX. Another MACC, not \textit{true} was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/budget_macc.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_budget}
\end{figure}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/threshold_macc.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:MACC_budget}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale=2.3]{figures/sample_sequence.eps}
    \caption{Each scenario iterated through 256 combinations of strategy implementation.}
    \label{fig:sample_sequence}
\end{figure}

@@

\subsubsection*{Retrofit and New Development Trajectory}
The majority of Wesbrook has been completed as of 2020, with 50\% of the total expected build-out of 725,925 sqm. remaining between now and the mid-21st century. As indicated in Figure \ref{fig:wesbrook_base} the yet-to-be-completed development will be assessed in the model through the future periods. While in less centrally planned and developed communities tackling development uncertainty would require a more thorough economic model, the Wesbrook planning and development scheme is well laid out in master-planning documents \citep{Wesbrook masterplan}. The simulation framework is built from a baseline in 2020 of the completed development up to 2020. Two more time periods were simulated, the first in 2050 and then in 2080. The base-case for each time period assumes that the stock of buildings that were simulated in the previous time-step (existing) were retrofitted with similarly performing technologies and components. New buildings are however built to a performance profile modeled after the changes in the municipalities building performance code (\citep{REAP}). While it is expected that the future will hold more advanced technologies, code development is capped at the introduction of the NZER requirements.

% \begin{table*}[h]
%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
%     \caption{The first two-column table.}
%     \label{tab:code_trajectory}
%     \centering
%     \begin{tabular}{ | c | c | c | }
%         \hline
%         \bf{Year} & \bf{Code Name} 2 & \bf{Performance Note} \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%         2005 & REAP2.1 & Wall U-Value = 0.4 W/m²K \\
%         \hline
%     \end{tabular}
%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
% \end{table*}

@@

The UBEMs are low-level of detail geometrically described by their heights above and below ground, window to wall ratio, and composition of envelope, HVAC, and energy supply traits.

% \begin{table}[ht]
%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
%     \caption{Example of a table.}
%     \label{tab:model_parameters}
%     \centering
%     \begin{tabular}{| c | c | c | }
%         \hline
%         \bf{Heading 1} & \bf{Heading} 2 & \bf{Heading 3} \\
%         \hline
%         Entry 1 & Entry 2 & Entry 3 \\
%         \hline
%     \end{tabular}
%     \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
% \end{table}

@@

%---------------------------------------------------------------------------------------
\section*{Results}
The simulation procedure was executed for 1024 iterations, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, \ref{fig:MACC_true_noDH}, and \ref{fig:MACC_true_DH}. These are discussed at more in the following sections but differ in that they are constructed following two logics. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in Figures \ref{fig:MACC_true_noDH_waterfall} and \ref{fig:MACC_true_DH_waterfall}.

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/budget_macc.eps}
    \caption{Illustrative MACC made assuming a budget of \$11 million in net cost was permitted for any plotted strategy-set.}
    \label{fig:MACC_budget}
\end{figure}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1]{figures/threshold_macc.eps}
    \caption{Illustrative MACC made assuming an emissions reduction threshold of 80\% was necessary for any plotted strategy-set.}
    \label{fig:MACC_threshold}
\end{figure}

\subsection*{General Performance}
Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios. Climate change does not appear to have a large impact on decarbonisation efforts. A warmer climate may even contribute to more emissions-performance at a lower cost.

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1.0]{figures/general_results.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

@@

MACCs were drawn as another form of visualising decision making. Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the bars. However, it improves on previous \textit{illustrative} MACCs in that the bars do not unnecessarily represent single strategy interventions, but rather a set of strategies. It was drawn to assist in planning under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies. The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting XXX. Another \textit{illustrative} MACC was drawn, seen in Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.
